---
title: "Dog_pupil_mimicry_Tobii"
author: "Lucrezia Lonardo"
date: "2024-02-28"
output: html_document
---
## Load packages
```{r }
rm(list=ls())
library(tidyverse)
load("~/GitHub/dog_pupil_mimicry/workspaces/Tobii_workspace.RData")
```

## Load data

```{r}
#Load data with Tobii "Fixation" gaze filter and pupil "noise reduction" filter

all.data<-
  read_tsv("./data/Dog_pupil_mimicry_10_04_2024_AOI_based_gazefilterfixation_incl_glance.tsv") %>% 
  mutate(Recording=as.factor(Recording)) %>% 
  mutate(Participant=as.factor(Participant)) %>% 
  mutate(Timeline=as.factor(Timeline)) %>% 
  filter(Recording!="Recording48" & Recording!="Recording55" & Recording!="Recording56" & Recording!="Recording57" & Recording!="Recording58" & Recording!="Recording60" & Recording!="Recording68" & Recording!="Recording69" & Recording!="Recording70" & Recording!="Recording71" & Recording!="Recording72" & Recording!="Recording74" & Recording!="Recording75" & Recording!="Recording77" & Recording!="Recording78" & Recording!="Recording80" & Recording!="Recording81" & Recording!="Recording101" & Recording!="Recording105" & Recording!="Recording107" & Recording!="Recording108" & Recording!="Recording109" & Recording!="Recording119" & Recording!="Recording121" & Recording!="Recording124" & Recording!="Recording125" & Recording!="Recording126" & Recording!="Recording127" & Recording!="Recording128" & Recording!="Recording131" & Recording!="Recording137" & Recording!="Recording156" & Recording!="Recording158" & Recording!="Recording160" & Recording!="Recording161" & Recording!="Recording162" & Recording!="Recording164" & Recording!="Recording165" & Recording!="Recording170" & Recording!="Recording172" & Recording!="Recording175" & Recording!="Recording177" & Recording!="Recording180" & Recording!="Recording188" & Recording!="Recording189" & Recording!="Recording193" & Recording!="Recording194" & Recording!="Recording195" & Recording!="Recording210" & Recording!="Recording221" & Recording!="Recording244" & Recording!="Recording231" & Recording!="Recording248" & Recording!="Recording251" & Recording!="Recording252" & Recording!="Recording259" & Recording!="Recording260" & Recording!="Recording299" & Recording!="Recording305" & Recording!="Recording307" & Recording!="Recording310" & Recording!="Recording348" & Recording!="Recording349" & Recording!="Recording350" & Recording!="Recording351" & Recording!="Recording352" & Recording!="Recording353" & Recording!="Recording354" & Recording!="Recording356" & Recording!="Recording357" & Recording!="Recording358" & Recording!="Recording359" & Recording!="Recording360" & Recording!="Recording362" & Recording!="Recording363" & Recording!="Recording372" & Recording!="Recording359" & Recording!="Recording369" & Recording!="Recording393") %>% # Sessions to be excluded (if not already excluded from project) as they were collected again with lower data loss
droplevels()


nova.data<-read_tsv("./data/Learning_Metrics.tsv") %>%  
  mutate(Recording=as.factor(Recording)) %>% 
  mutate(Participant=as.factor(Participant)) %>% 
  mutate(Timeline=as.factor(Timeline))
```

```{r}
#figure out which trials to filter out, because they were repeated with lower data loss
trials.to.exclude<-c( 
which(all.data$Recording=="Recording52" & all.data$TOI=="d03-dilating"),
which(all.data$Recording=="Recording53" & all.data$TOI=="h08-dilating"),
which(all.data$Recording=="Recording61" & all.data$TOI=="b03-dilating"),
which(all.data$Recording=="Recording159" & all.data$TOI=="b06-constr"),
which(all.data$Recording=="Recording116" & all.data$TOI=="h14-constr"),
which(all.data$Recording=="Recording140" & all.data$TOI=="d14-dilating"),
which(all.data$Recording=="Recording196" & all.data$TOI=="b07-constr"),
which(all.data$Recording=="Recording286" & all.data$TOI=="b08-dilating"),
which(all.data$Recording=="Recording211" & all.data$TOI=="d02-constr"),
which(all.data$Recording=="Recording254" & all.data$TOI=="h15-dilating"),
which(all.data$Recording=="Recording280" & all.data$TOI=="h00-dilating"),
which(all.data$Recording=="Recording247" & all.data$TOI=="h08-dilating"),
which(all.data$Recording=="Recording250" & all.data$TOI=="h02-constr"),
which(all.data$Recording=="Recording164" & all.data$TOI=="d07-dilating"),
which(all.data$Recording=="Recording250" & all.data$TOI=="b05-constr"),
which(all.data$Recording=="Recording110" & all.data$TOI=="d10-dilating"),
which(all.data$Recording=="Recording288" & all.data$TOI=="d13-dilating"),
which(all.data$Recording=="Recording279" & all.data$TOI=="h01-constr"),
which(all.data$Recording=="Recording218" & all.data$TOI=="h09-dilating"),
which(all.data$Recording=="Recording273" & all.data$TOI=="b02-constr"),
which(all.data$Recording=="Recording157" & all.data$TOI=="d04-constr"),
which(all.data$Recording=="Recording166" & all.data$TOI=="d01-constr"),
which(all.data$Recording=="Recording191" & all.data$TOI=="b14-constr"),
which(all.data$Recording=="Recording195" & all.data$TOI=="b09-constr"),
which(all.data$Recording=="Recording197" & all.data$TOI=="h14-constr"),
which(all.data$Recording=="Recording275" & all.data$TOI=="d00-constr"),
which(all.data$Recording=="Recording287" & all.data$TOI=="b10-dilating"),
which(all.data$Recording=="Recording212" & all.data$TOI=="b14-constr"),
which(all.data$Recording=="Recording234" & all.data$TOI=="h15-constr"),
which(all.data$Recording=="Recording294" & all.data$TOI=="b14-dilating"),
which(all.data$Recording=="Recording238" & all.data$TOI=="d08-constr"),
which(all.data$Recording=="Recording206" & all.data$TOI=="h13-dilating"),
which(all.data$Recording=="Recording204" & all.data$TOI=="d04-constr"),
which(all.data$Recording=="Recording224" & all.data$TOI=="h12-constr"),
which(all.data$Recording=="Recording295" & all.data$TOI=="h13-constr"),
which(all.data$Recording=="Recording292" & all.data$TOI=="h14-dilating"),
which(all.data$Recording=="Recording215" & all.data$TOI=="d11-dilating"),
which(all.data$Recording=="Recording230" & all.data$TOI=="b14-dilating"),
which(all.data$Recording=="Recording302" & all.data$TOI=="d08-constr"),
which(all.data$Recording=="Recording330" & all.data$TOI=="b14-constr"),
which(all.data$Recording=="Recording325" & all.data$TOI=="b13-dilating"),
which(all.data$Recording=="Recording322" & all.data$TOI=="d13-dilating"),
which(all.data$Recording=="Recording169" & all.data$TOI=="d05-dilating"),
which(all.data$Recording=="Recording285" & all.data$TOI=="h03-dilating"),
which(all.data$Recording=="Recording286" & all.data$TOI=="d02-constr"),
which(all.data$Recording=="Recording289" & all.data$TOI=="h02-constr"),
which(all.data$Recording=="Recording321" & all.data$TOI=="d12-dilating"),
which(all.data$Recording=="Recording329" & all.data$TOI=="d00-constr"),
which(all.data$Recording=="Recording282" & all.data$TOI=="d13-constr"),
which(all.data$Recording=="Recording342" & all.data$TOI=="b13-constr"),
which(all.data$Recording=="Recording381" & all.data$TOI=="h13-constr"),
which(all.data$Recording=="Recording394" & all.data$TOI=="d12-dilating"), #added this and lines below on
which(all.data$Recording=="Recording367" & all.data$TOI=="h05-dilating"), #10/04
which(all.data$Recording=="Recording392" & all.data$TOI=="b08-dilating"),
which(all.data$Recording=="Recording375" & (all.data$TOI=="d01-dilating" |
all.data$TOI=="b00-dilating")),                                           #until here
which(all.data$Recording=="Recording51" & (all.data$TOI=="d14-constr" |
all.data$TOI=="h07-dilating")),
which(all.data$Recording=="Recording66" & (all.data$TOI=="d01-constr" |
all.data$TOI=="h01-dilating")),
which(all.data$Recording=="Recording88" & (all.data$TOI=="b01-dilating" |
all.data$TOI=="b03-constr")),
which(all.data$Recording=="Recording141" & (all.data$TOI=="b11-constr" |
all.data$TOI=="b10-dilating")),
which(all.data$Recording=="Recording181" & (all.data$TOI=="b02-constr" |
all.data$TOI=="h13-dilating")),
which(all.data$Recording=="Recording303" & (all.data$TOI=="h10-dilating"|
all.data$TOI=="d01-constr")),
which(all.data$Recording=="Recording312" & (all.data$TOI=="b05-dilating"| 
all.data$TOI=="h00-constr")),
which(all.data$Recording=="Recording318" & (all.data$TOI=="h08-dilating" | 
all.data$TOI=="b02-constr")),
which(all.data$Recording=="Recording321" & (all.data$TOI=="d01-dilating"| 
all.data$TOI=="b08-dilating")),
which(all.data$Recording=="Recording322" & (all.data$TOI=="h15-constr" |
all.data$TOI=="h01-constr")),                                              
which(all.data$Recording=="Recording326" & (all.data$TOI=="b11-dilating"| 
all.data$TOI=="h05-constr")),
which(all.data$Recording=="Recording327" & (all.data$TOI=="h06-constr" |
all.data$TOI=="d07-constr")),
which(all.data$Recording=="Recording328" & (all.data$TOI=="b11-constr"| 
all.data$TOI=="d00-dilating")),
which(all.data$Recording=="Recording329" & (all.data$TOI=="b08-constr"| 
all.data$TOI=="h03-constr")),
which(all.data$Recording=="Recording330" & (all.data$TOI=="b09-dilating"| 
all.data$TOI=="b10-dilating")),
which(all.data$Recording=="Recording331" & (all.data$TOI=="d07-dilating"| 
all.data$TOI=="d10-constr")),
which(all.data$Recording=="Recording338" & (all.data$TOI=="d14-dilating"| 
all.data$TOI=="b15-constr")),
which(all.data$Recording=="Recording290" & (all.data$TOI=="h03-constr"| 
all.data$TOI=="d14-constr")),
which(all.data$Recording=="Recording207" & (all.data$TOI=="b08-constr"| 
all.data$TOI=="b11-dilating")),
which(all.data$Recording=="Recording214" & (all.data$TOI=="h06-dilating" | all.data$TOI=="b03-dilating")),
which(all.data$Recording=="Recording227" & (all.data$TOI=="b06-dilating"| all.data$TOI=="h07-dilating")),
which(all.data$Recording=="Recording267" & (all.data$TOI=="h06-dilating" | all.data$TOI=="b03-dilating")),
which(all.data$Recording=="Recording288" & (all.data$TOI=="d10-dilating" | 
all.data$TOI=="b05-constr")),
which(all.data$Recording=="Recording256" & (all.data$TOI=="h09-dilating" | 
all.data$TOI=="h15-dilating"| all.data$TOI=="h09-constr")),
which(all.data$Recording=="Recording254" & (all.data$TOI=="h09-dilating" | 
all.data$TOI=="h09-constr")),
which(all.data$Recording=="Recording218" & (all.data$TOI=="h09-constr" | 
all.data$TOI=="h15-dilating")),
which(all.data$Recording=="Recording246" & all.data$TOI=="h02-dilating"),
which(all.data$Recording=="Recording166" & (all.data$TOI=="b14-dilating" | 
all.data$TOI=="d11-constr")),
which(all.data$Recording=="Recording123" & (all.data$TOI=="b06-constr"| 
all.data$TOI=="d03-dilating")),
which(all.data$Recording=="Recording200" & (all.data$TOI=="b02-dilating"| 
all.data$TOI=="h12-dilating")),
which(all.data$Recording=="Recording253" & all.data$TOI=="d01-constr"),
which(all.data$Recording=="Recording220" & (all.data$TOI=="b05-dilating" | 
all.data$TOI=="h10-dilating")),
which(all.data$Recording=="Recording257" & all.data$TOI=="d12-constr"),
which(all.data$Recording=="Recording255" & (all.data$TOI=="d07-constr" | 
all.data$TOI=="d12-dilating")),
which(all.data$Recording=="Recording219" & all.data$TOI=="h12-constr"),
which(all.data$Recording=="Recording247" & (all.data$TOI=="b02-constr" | 
all.data$TOI=="d03-constr")),
which(all.data$Recording=="Recording304" & (all.data$TOI=="d01-constr"| 
all.data$TOI=="d12-constr")),
which(all.data$Recording=="Recording306" & (all.data$TOI=="d10-constr"| 
all.data$TOI=="h08-constr")),
which(all.data$Recording=="Recording308" & (all.data$TOI=="b05-constr"| 
all.data$TOI=="h06-constr")),
which(all.data$Recording=="Recording339" & (all.data$TOI=="b00-constr"| 
all.data$TOI=="d07-constr")),
which(all.data$Recording=="Recording265" & (all.data$TOI=="d08-dilating" |
all.data$TOI=="b05-constr" | all.data$TOI=="h07-constr")),
which(all.data$Recording=="Recording87" & (all.data$TOI=="b09-constr" |
all.data$TOI=="h13-constr" | all.data$TOI=="h15-constr" | all.data$TOI=="b05-constr")),
which(all.data$Recording=="Recording242" & 
(all.data$TOI=="d04-dilating" | all.data$TOI=="b07-dilating"| all.data$TOI=="d14-constr"| all.data$TOI=="d15-constr"| all.data$TOI=="h05-constr")),
which(all.data$Recording=="Recording241" & 
(all.data$TOI=="b06-dilating" | all.data$TOI=="b15-dilating"| all.data$TOI=="b01-constr"| all.data$TOI=="b12-constr"| all.data$TOI=="h01-dilating")),
which(all.data$Recording=="Recording240" & 
(all.data$TOI=="d02-dilating" | all.data$TOI=="d09-dilating"| all.data$TOI=="h12-constr")),
which(all.data$Recording=="Recording324" & 
(all.data$TOI=="b01-constr" | all.data$TOI=="d05-constr"| all.data$TOI=="h08-constr")),
which(all.data$Recording=="Recording133" & all.data$TOI=="h11-constr"),
which(all.data$Recording=="Recording204" & 
(all.data$TOI=="b13-constr" | 
all.data$TOI=="h08-constr")),
which(all.data$Recording=="Recording243" & all.data$TOI=="d04-constr"),
which(all.data$Recording=="Recording228" & 
(all.data$TOI=="h00-constr" | all.data$TOI=="h10-constr")),
which(all.data$Recording=="Recording229" & all.data$TOI=="h15-constr"),
which((all.data$Recording=="Recording54"| all.data$Recording=="Recording327") & all.data$TOI=="d06-constr"),
which((all.data$Recording=="Recording54"| all.data$Recording=="Recording327") & all.data$TOI=="d06-constr"),
which((all.data$Recording=="Recording279"| all.data$Recording=="Recording322") & all.data$TOI=="h15-constr"),
which((all.data$Recording=="Recording325"| all.data$Recording=="Recording352") & all.data$TOI=="h02-dilating"),
which((all.data$Recording=="Recording325"| all.data$Recording=="Recording323") & all.data$TOI=="b03-constr"),
which((all.data$Recording=="Recording53" | all.data$Recording=="Recording86" | all.data$Recording=="Recording139" | all.data$Recording=="Recording266" | all.data$Recording=="Recording273") & all.data$TOI=="d03-constr"),
which((all.data$Recording=="Recording266"| all.data$Recording=="Recording142"| all.data$Recording=="Recording267") & all.data$TOI=="d13-constr"),
which((all.data$Recording=="Recording338"| all.data$Recording=="Recording342"| all.data$Recording=="Recording192") & all.data$TOI=="h13-constr"),
which((all.data$Recording=="Recording339"| all.data$Recording=="Recording341"| all.data$Recording=="Recording225") & all.data$TOI=="b01-dilating"),
which((all.data$Recording=="Recording94"| all.data$Recording=="Recording149"| all.data$Recording=="Recording92") & 
(all.data$TOI=="h01-constr"| all.data$TOI=="h05-constr")),
which((all.data$Recording=="Recording94"| all.data$Recording=="Recording149"| all.data$Recording=="Recording93") & (all.data$TOI=="b04-dilating" | all.data$TOI=="b12-dilating")),
which((all.data$Recording=="Recording94"| all.data$Recording=="Recording149") & (all.data$TOI=="h03-constr" | all.data$TOI=="d01-constr")),
which((all.data$Recording=="Recording266"| all.data$Recording=="Recording267") & all.data$TOI=="h06-dilating"),
which((all.data$Recording=="Recording148"| all.data$Recording=="Recording266") & all.data$TOI=="h08-constr"),
which((all.data$Recording=="Recording263"| all.data$Recording=="Recording266"| all.data$Recording=="Recording142") & all.data$TOI=="h11-constr"),
which((all.data$Recording=="Recording209" | all.data$Recording=="Recording293"| all.data$Recording=="Recording297") & all.data$TOI=="b08-dilating"),
which((all.data$Recording=="Recording297"| all.data$Recording=="Recording293"| all.data$Recording=="Recording238") & all.data$TOI=="d08-constr"),
which((all.data$Recording=="Recording294"| all.data$Recording=="Recording293"| all.data$Recording=="Recording238") & all.data$TOI=="b14-dilating"),
which((all.data$Recording=="Recording296"| all.data$Recording=="Recording202") & all.data$TOI=="d06-dilating"),
which((all.data$Recording=="Recording296"| all.data$Recording=="Recording136") & all.data$TOI=="b13-dilating"),
which((all.data$Recording=="Recording292"| all.data$Recording=="Recording241") & all.data$TOI=="b06-dilating"),
which((all.data$Recording=="Recording292"| all.data$Recording=="Recording241") & all.data$TOI=="b15-dilating"),
which((all.data$Recording=="Recording298"| all.data$Recording=="Recording292"| all.data$Recording=="Recording241") & all.data$TOI=="b12-constr"),
which(all.data$Recording=="Recording142" & (all.data$TOI=="d02-dilating" | all.data$TOI=="d13-constr"| all.data$TOI=="h11-constr")),
which(all.data$Recording=="Recording263" & (all.data$TOI=="b07-dilating" | all.data$TOI=="b09-dilating"| all.data$TOI=="b11-dilating")),
which(all.data$Recording=="Recording264" & (all.data$TOI=="b01-constr" | 
all.data$TOI=="b04-constr")),
which(all.data$Recording=="Recording261" & (all.data$TOI=="d02-constr" | all.data$TOI=="d12-constr"| all.data$TOI=="h14-dilating"| all.data$TOI=="d14-constr")),
#which(all.data$Recording=="Recording310" & (all.data$TOI=="b00-dilating" | all.data$TOI=="b15-constr"| all.data$TOI=="d14-dilating" | all.data$TOI=="h07-constr" | all.data$TOI=="h13-constr")),
which(all.data$Recording=="Recording133" & (all.data$TOI=="b07-dilating" | all.data$TOI=="d04-dilating"| all.data$TOI=="d15-constr")),
which(all.data$Recording=="Recording146" & (all.data$TOI=="b07-constr" | 
all.data$TOI=="d05-constr")),
which(all.data$Recording=="Recording333" & (all.data$TOI=="d06-dilating" | all.data$TOI=="h08-dilating"| all.data$TOI=="b03-dilating"| all.data$TOI=="h13-dilating")),
which(all.data$Recording=="Recording213" & (all.data$TOI=="b04-constr" | all.data$TOI=="d02-dilating")),
which(all.data$Recording=="Recording216" & (all.data$TOI=="d09-constr" | all.data$TOI=="h01-dilating")),
which(all.data$Recording=="Recording112" & (all.data$TOI=="d04-dilating" | all.data$TOI=="b06-dilating")),
which(all.data$Recording=="Recording73" & (all.data$TOI=="d15-constr" | all.data$TOI=="h02-constr")),
which(all.data$Recording=="Recording111" & (all.data$TOI=="h15-constr" | all.data$TOI=="h14-dilating")),
which(all.data$Recording=="Recording191" & (all.data$TOI=="h07-constr" | all.data$TOI=="b00-dilating")),
which(all.data$Recording=="Recording253" & (all.data$TOI=="b14-dilating" | all.data$TOI=="d11-constr")),
which(all.data$Recording=="Recording276" & (all.data$TOI=="d15-constr" | all.data$TOI=="b12-dilating")),
which(all.data$Recording=="Recording155" & (all.data$TOI=="b08-constr" | all.data$TOI=="h03-constr")),
which(all.data$Recording=="Recording235" & (all.data$TOI=="d10-constr" | all.data$TOI=="h06-dilating")),
which(all.data$Recording=="Recording296" & (all.data$TOI=="b06-dilating" | all.data$TOI=="d06-dilating"| all.data$TOI=="b13-dilating"| all.data$TOI=="h15-constr"| all.data$TOI=="b15-dilating")))


all.data<-all.data %>%  filter(!row_number() %in% trials.to.exclude)
  

all.data.toi<-all.data %>% 
  filter(TOI!="Entire Recording") %>% 
  droplevels() %>% 
  mutate(condition=ifelse(grepl("constr", TOI), "constricting", ifelse(grepl("dilating", TOI), "dilating", "grey_screen")))

nova.data.toi<-nova.data%>% 
  filter(TOI!="Entire Recording") %>% 
  filter(Recording!="test w lucrezia") %>% 
  droplevels() %>% 
  mutate(condition=ifelse(grepl("constr", TOI), "constricting", ifelse(grepl("dilating", TOI), "dilating", "grey_screen")))
```

## Explore data

```{r}
str(all.data.toi)
levels(as.factor(all.data.toi$Recording))
table(all.data.toi$Participant, all.data.toi$Recording)
levels(as.factor(all.data.toi$TOI))
levels(as.factor(all.data.toi$Timeline))

#check how many trials were collected with each dog
all.data.toi.trials<-all.data.toi %>% 
  filter(TOI!="grey_screen") %>% 
#mutate(N_trials_collected=count(Participant)) alternative to what is below
  group_by(Participant) %>% 
  summarise(N_trials_collected=n())
```
##Explore Nova's data
```{r}
str(nova.data.toi)
levels(as.factor(nova.data.toi$Recording))
table(nova.data.toi$Participant, nova.data.toi$Recording)
levels(as.factor(nova.data.toi$TOI))
levels(as.factor(nova.data.toi$Timeline))
nova.data.toi$TOI[nova.data.toi$Timeline=="Nova 11th session"] #d08-constr missing


#check how many trials were collected with Nova
nova.data.toi.trials<-nova.data.toi %>% 
  filter(!grepl("Grey screen", TOI)) %>% 
#mutate(N_trials_collected=count(Participant)) alternative to what is below
  group_by(Participant) %>% 
  summarise(N_trials_collected=n()) #Nova has 101 trials
```

##Individual checks to see if there are repeated trials
```{r}
####Kaije
#check how many trials per dog
all.data.toi.trials.kaije<-all.data.toi %>% 
  filter(TOI!="grey_screen") %>% 
  filter(Participant=="kaije") %>% 
  droplevels()
length(all.data.toi.trials.kaije$TOI) 

levels(as.factor(all.data.toi.trials.kaije$TOI)) #which videos did the dog see?
  #mutate(N_trials_collected=count(Participant))
  # group_by(Participant) %>% 
  # summarise(N_trials_collected=n())

all.data.toi.trials.kaije$TOI
#which trials are duplicates?
which(duplicated(all.data.toi.trials.kaije$TOI)==TRUE)

#### Noodle
#check how many trials per dog
all.data.toi.trials.noodle<-all.data.toi %>% 
  filter(TOI!="grey_screen") %>% 
  filter(Participant=="Noodle") %>% 
  droplevels()
length(all.data.toi.trials.noodle$TOI) 

#which videos did the dog see?
levels(as.factor(all.data.toi.trials.noodle$TOI)) 


#### Pepe
#check how many trials per dog
all.data.toi.trials.pepe<-all.data.toi %>% 
  filter(TOI!="grey_screen") %>% 
  filter(Participant=="Pepe") %>% 
  droplevels()
length(all.data.toi.trials.pepe$TOI) 

#which videos did the dog see?
levels(as.factor(all.data.toi.trials.pepe$TOI)) 


#### Barney
#check how many trials per dog
all.data.toi.trials.barney<-all.data.toi %>% 
  filter(TOI!="grey_screen") %>% 
  filter(Participant=="Barney") %>% 
  droplevels()
length(all.data.toi.trials.barney$TOI) 

#which videos did the dog see?
levels(as.factor(all.data.toi.trials.barney$TOI)) 
```

##calculate % tracked (i.e., detected) gaze for each trial. Using the data with the Tobii "Fixation" gaze filter and the Total duration of fixations
```{r}
tracked.gaze.data<-all.data.toi %>% 
  filter(TOI!="grey_screen") %>% 
  mutate(percent_tracked_gaze=(Total_duration_of_fixations/Duration_of_interval)*100) %>% 
  mutate(percent_tracked_glances=(Total_duration_of_Glances/Duration_of_interval)*100)

#using glances instead of fixations results in the gaze being detected for longer
summary(tracked.gaze.data$percent_tracked_gaze)
summary(tracked.gaze.data$percent_tracked_glances)
sum(tracked.gaze.data$percent_tracked_gaze<tracked.gaze.data$percent_tracked_glances)
sum(tracked.gaze.data$percent_tracked_gaze>tracked.gaze.data$percent_tracked_glances)
sum(tracked.gaze.data$percent_tracked_gaze==tracked.gaze.data$percent_tracked_glances)

#potentially replace Total_duration_of_fixations with Total_duration_of_Glances.
#However for now I continue with fixations (the more conservative measure)

#only select relevant columns
tracked.gaze.data.red<-tracked.gaze.data %>% 
  select(c(Recording:Media, Average_pupil_diameter, Total_duration_of_Glances, condition, percent_tracked_gaze, percent_tracked_glances)) %>% 
  droplevels()
  
#Trials to be excluded
##gaze
tracked.gaze.data.red.to.be.excluded<-tracked.gaze.data.red %>% 
group_by(Participant) %>% 
summarise(percent_trials_excluded=sum(percent_tracked_gaze<50)/length(percent_tracked_gaze))

##glances
tracked.glances.data.red.to.be.excluded<-tracked.gaze.data.red %>% 
group_by(Participant) %>% 
summarise(percent_trials_excluded=sum(percent_tracked_glances<50)/length(percent_tracked_glances))
```


```{r}
#For Nova:
pattern <- "(constr|dilating).*"

#LL: 23/05 continue from here:
tracked.gaze.data.nova<-nova.data.toi %>% 
 filter(!grepl("Grey screen", TOI)) %>% 
 mutate(TOI= as_factor(str_replace_all(as.character(TOI), pattern, "\\1"))) %>% 
 mutate(percent_tracked_gaze=(Total_duration_of_fixations/Duration_of_interval)*100) %>% 
 mutate(percent_tracked_glances=(Total_duration_of_Glances/Duration_of_interval)*100)



#using glances instead of fixations results in the gaze being detected for longer
summary(tracked.gaze.data.nova$percent_tracked_gaze)
summary(tracked.gaze.data.nova$percent_tracked_glances)
sum(tracked.gaze.data.nova$percent_tracked_gaze<tracked.gaze.data.nova$percent_tracked_glances)
sum(tracked.gaze.data.nova$percent_tracked_gaze>tracked.gaze.data.nova$percent_tracked_glances)
sum(tracked.gaze.data.nova$percent_tracked_gaze==tracked.gaze.data.nova$percent_tracked_glances)

#potentially replace Total_duration_of_fixations with Total_duration_of_Glances.
#However for now I continue with fixations (the more conservative measure)

#only select relevant columns
tracked.gaze.data.red.nova<-tracked.gaze.data.nova %>% 
  select(c(Recording:Media, Average_pupil_diameter, Total_duration_of_Glances, condition, percent_tracked_gaze, percent_tracked_glances)) %>% 
  droplevels()
  
##ADD HERE FULL-JOIN WITH OTHER DOGS?

#Trials to be excluded
##gaze
tracked.gaze.data.red.to.be.excluded<-tracked.gaze.data.red %>% 
group_by(Participant) %>% 
summarise(percent_trials_excluded=sum(percent_tracked_gaze<50)/length(percent_tracked_gaze))

##glances
tracked.glances.data.red.to.be.excluded<-tracked.gaze.data.red %>% 
group_by(Participant) %>% 
summarise(percent_trials_excluded=sum(percent_tracked_glances<50)/length(percent_tracked_glances))
```

##check if there are repeated sessions, to only keep trials with higher % tracked gaze 
```{r}
#Kaije
tracked.gaze.data.red.kaije<-tracked.gaze.data.red %>% 
  filter(Participant=="kaije")
which(duplicated(tracked.gaze.data.red.kaije$TOI)==TRUE)

#Noodle
tracked.gaze.data.red.noodle<-tracked.gaze.data.red %>% 
  filter(Participant=="Noodle")
which(duplicated(tracked.gaze.data.red.noodle$TOI)==TRUE)

#Pepe
tracked.gaze.data.red.pepe<-tracked.gaze.data.red %>% 
  filter(Participant=="Pepe")
which(duplicated(tracked.gaze.data.red.pepe$TOI)==TRUE)

#Messi
tracked.gaze.data.red.messi<-tracked.gaze.data.red %>% 
  filter(Participant=="Messi")
which(duplicated(tracked.gaze.data.red.messi$TOI)==TRUE)

#Barney
tracked.gaze.data.red.barney<-tracked.gaze.data.red %>% 
  filter(Participant=="Barney")
which(duplicated(tracked.gaze.data.red.barney$TOI)==TRUE)

#Jazz
tracked.gaze.data.red.jazz<-tracked.gaze.data.red %>% 
  filter(Participant=="jazz")
which(duplicated(tracked.gaze.data.red.jazz$TOI)==TRUE)
#find out which recordings belong to Jazz, to exclude them from analyses 
sort(unique(tracked.gaze.data.red.jazz$Recording))
```


```{r}
####check which trials should be repeated for each dog

#Barney
to.be.repeated.Barney<-tracked.gaze.data.red %>% 
filter(percent_tracked_gaze<50) %>% 
filter(Participant=="Barney")

#Messi
to.be.repeated.Messi<-tracked.gaze.data.red %>% 
filter(percent_tracked_gaze<50) %>% 
filter(Participant=="Messi")

#Kaije
to.be.repeated.Kaije<-tracked.gaze.data.red %>% 
filter(percent_tracked_gaze<50) %>% 
filter(Participant=="kaije")

#Noodle
to.be.repeated.Noodle<-tracked.gaze.data.red %>% 
filter(percent_tracked_gaze<50) %>% 
filter(Participant=="Noodle")

#Pepe
to.be.repeated.Pepe<-tracked.gaze.data.red %>% 
filter(percent_tracked_gaze<50) %>% 
filter(Participant=="Pepe")

#Jazz
to.be.repeated.Jazz<-tracked.gaze.data.red %>% 
filter(percent_tracked_gaze<50) %>% 
filter(Participant=="jazz")
```

##import the preprocessed pupillometry data 
```{r}
#Tobii gaze fixation and pupil noise reduction filters applied to the data. Then, data pre-processed using the physiodata toolbox, using the default settings. Then data resampled to 1 Hz
#Variable Both_pupil contains resampled pupil size in mm for both eyes
library(readxl)

prepr.pupil.data<-read_excel("./data/PhysioEpochsResampled_10Hz_20240424_human_pupil_parameters.xlsx", skip = 4, col_names=TRUE) %>%  #filter out first 4 rows (before headings)
 separate(Sample_ID, into = c("Physioanalyzer_Period_of_Recording", "Recording", "Time"), sep = " ") %>% 
 mutate(Recording= gsub("\\(Project2_|\\)", "", Recording)) %>% 
 mutate(Time= gsub("\\(", "", Time)) %>% 
 filter(grepl("constr|dilating", epochName))

#add Participant info from Recording name
## Select only the "Recording" and "Participant" columns from tracked.gaze.data (to only keep periods with stimuli video presentation)
tracked.gaze.data.selected <- tracked.gaze.data [, c("Recording", "Participant")]

############################### until line 433 doesn't do the right thing #####################
prepr.pupil.data.merged <-merge(prepr.pupil.data.selected, tracked.gaze.data.red) %>%  
  filter(Participant!="jazz") %>% #did not meet inclusion criterion of at least 50% trials with at least 50% tracked gaze
  droplevels() %>% #LL: but here why do I get three values (rows) per 10 Hz? I should only have one row (one pupil size value) for each 10 ms interval
  group_by(Recording) %>% 
  distinct(Time, .keep_all = TRUE) %>% #Keep only the first row for each unique Time value within a recording and all columns
  #LL: I tried these two lines but they do not seem to be doing the right thing as for example in Recording 102 they do not keep all the values of time for the last two stimuli.
  mutate(stim_pupil_movement=ifelse(grepl("constr", epochName), "constricting", "dilating")) %>% 
  mutate(stim_species=ifelse(grepl("DIA_d", Physioanalyzer_Period_of_Recording), "dog", ifelse(grepl("DIA_b", Physioanalyzer_Period_of_Recording), "bonobo", ifelse(grepl("DIA_h", Physioanalyzer_Period_of_Recording), "human","NA"))))
  
levels(as.factor(prepr.pupil.data.merged$Participant))
rm(list=c("prepr.pupil.data.merged"))
#######################################################################
Recordings.Barney<-sort(unique(tracked.gaze.data.red.barney$Recording)) %>% 
  droplevels()
Recordings.Kaije<-sort(unique(tracked.gaze.data.red.kaije$Recording))%>% 
  droplevels()
Recordings.Messi<-sort(unique(tracked.gaze.data.red.messi$Recording))%>% 
  droplevels()
Recordings.Noodle<-sort(unique(tracked.gaze.data.red.noodle$Recording))%>% 
  droplevels()
Recordings.Pepe<-sort(unique(tracked.gaze.data.red.pepe$Recording))%>% 
  droplevels()

#number of recordings per dog
length(Recordings.Barney)
length(Recordings.Kaije)
length(Recordings.Messi)
length(Recordings.Noodle)
length(Recordings.Pepe)
#all recordings per dog
Recordings.Barney
Recordings.Kaije
Recordings.Messi
Recordings.Noodle
Recordings.Pepe

## Get independent variables 

#Subject
prepr.pupil.data1<-read_excel("./data/PhysioEpochsResampled_10Hz_20240424_human_pupil_parameters.xlsx", skip = 4, col_names=TRUE) %>% #filter out first 4 rows (before headings)
 separate(Sample_ID, into = c("Physioanalyzer_Period_Recording", "Time"), sep = "\\) \\(") %>% 
 #mutate(Recording= gsub("\\(Project2_|\\)", "", Recording)) %>% 
 mutate(Time= gsub("\\)|s", "", Time)) %>% 
 filter(grepl("constr|dilating", epochName)) %>% 
 mutate(Recording.nr = as.numeric(str_extract(Physioanalyzer_Period_Recording, "(?<=_Recording).*$"))) %>% 
 mutate(Recording=str_extract(Physioanalyzer_Period_Recording, "(?<=Project2_).*$")) %>% 
 mutate(Subject=ifelse(Recording %in% Recordings.Barney, "Barney", 
                 ifelse(Recording %in% Recordings.Pepe, "Pepe",
                 ifelse(Recording %in% Recordings.Kaije, "Kaije",
                 ifelse(Recording %in% Recordings.Messi, "Messi",
                 ifelse(Recording %in% Recordings.Noodle, "Noodle", "NA")))))) 
 

#Trial
prepr.pupil.data2<-prepr.pupil.data1 %>% 
 group_by(Physioanalyzer_Period_Recording, startTime, Recording.nr, Subject, startActualValue) %>% 
  summarise(Trial = n()) %>% 
  group_by(Subject) %>% 
  arrange(Recording.nr, startTime) %>%
  summarise(Trial=row_number(),
            startActualValue = startActualValue,
            startTime = startTime,
            Recording.nr = Recording.nr) 

#Lagged time
prepr.pupil.data3<-prepr.pupil.data1 %>% 
  group_by(Subject, Physioanalyzer_Period_Recording) %>% 
  mutate(Time_minus_one=lag(Time, default=NA)) %>% #Add Time-1 to account for autocorrelation 
  ungroup()

#Condition (stim_pupil_movement) and stimulus species
prepr.pupil.data4<-full_join(prepr.pupil.data1, prepr.pupil.data2) %>% 
  full_join(prepr.pupil.data3) %>% 
  mutate(Stim_pupil_movement=ifelse(grepl("constr", epochName), "constricting", 
                                          ifelse(grepl("dilating", epochName), "dilating", NA))) %>% 
  mutate(Stim_species=ifelse(grepl("DIA_d", Physioanalyzer_Period_Recording), "dog", ifelse(grepl("DIA_b", Physioanalyzer_Period_Recording), "bonobo", ifelse(grepl("DIA_h", Physioanalyzer_Period_Recording), "human","NA")))) %>% 
  mutate(Time=as.numeric(Time)) %>% 
   mutate(Time_minus_one=as.numeric(Time_minus_one)) 

  # determine baseline
baseline.end=1.25 #(1250 ms = 1.25 s)
pupil.baseline <- prepr.pupil.data4 %>%
  filter(Time < baseline.end & Time > 0) %>% 
  group_by(Subject, Stim_pupil_movement) %>%
  summarise(median.base.pupil = median(Both_Pupil, na.rm = TRUE))

#perform subtractive baseline correction
prepr.pupil.data <- prepr.pupil.data4 %>%
  group_by(Subject, Stim_pupil_movement, Trial) %>%
  full_join(pupil.baseline) %>% #add baseline data
  mutate(pupil.base.corrected = Both_Pupil - median.base.pupil)%>% #subtractive baseline correction
  ungroup()

##LL: STILL TO DO: filter the data to only keep 4 seconds from end baseline 1.25 until 5.25 s!!!
```
#fit multilevel model with polynomials
```{r}
library(lme4)
mm1.tobii.full.int<-lmer(Both_Pupil ~ 1 + Stim_pupil_movement*Stim_species + Time + Time_minus_one + I(Time^2)+ I(Time^3) + 
                  Time:Stim_species + I(Time^2):Stim_species + I(Time^3):Stim_species + 
                  Time:Stim_pupil_movement + I(Time^2):Stim_pupil_movement + I(Time^3):Stim_pupil_movement +
                  Time:Stim_species:Stim_pupil_movement + I(Time^2):Stim_species:Stim_pupil_movement + I(Time^3):Stim_species:Stim_pupil_movement +
                  (1 | Subject/Trial),  
                  data=prepr.pupil.data, REML=F)
#fixed-effect model matrix is rank deficient so dropping 1 column / coefficient

mm1.tobii.null<-lmer(Both_Pupil ~ 1 + Time + Time_minus_one + I(Time^2)+ I(Time^3) +
                  (1 | Subject/Trial),  
                  data=prepr.pupil.data, REML=F)

#fixed-effect model matrix is rank deficient so dropping 1 column / coefficient
```
```{r}
as.data.frame(anova(mm1.tobii.null, mm1.tobii.full, test="Chisq")) #full-null model comparison is significant (Chisq.=61.99, Df=12, P<.001)	
```


```{r}
#Results
summary(mm1.tobii.full.int)$coefficients
```

```{r}
# for an LMM, P-values for the individual fixed effects are most reliable when obtained using the Satterthwaite approximation
# for a model based on REML (Luke 2017)
library(lmerTest)

mm1.tobii.full.int.reml = lmerTest::lmer(Both_Pupil ~ 1 + Stim_pupil_movement*Stim_species + Time + Time_minus_one + I(Time^2)+ I(Time^3) + 
                  Time:Stim_species + I(Time^2):Stim_species + I(Time^3):Stim_species + 
                  Time:Stim_pupil_movement + I(Time^2):Stim_pupil_movement + I(Time^3):Stim_pupil_movement +
                  Time:Stim_species:Stim_pupil_movement + I(Time^2):Stim_species:Stim_pupil_movement + I(Time^3):Stim_species:Stim_pupil_movement +
                  (1 | Subject/Trial),  
                  data=prepr.pupil.data, REML=T)

round(summary(mm1.tobii.full.int.reml)$coefficients, 3)


# to get an overall test of the interaction, compare the full model with a reduced model not comprising
# the interaction between species and condition
# fit the reduced model not comprising the interaction between species
# and condition:
library(lme4)
mm1.tobii.red.int=lmer(Both_Pupil ~ 1 + Time + Time_minus_one + I(Time^2)+ I(Time^3) + 
                  Time:Stim_species + I(Time^2):Stim_species + I(Time^3):Stim_species + 
                  Time:Stim_pupil_movement + I(Time^2):Stim_pupil_movement + I(Time^3):Stim_pupil_movement +
                  Time:Stim_species:Stim_pupil_movement + I(Time^2):Stim_species:Stim_pupil_movement + I(Time^3):Stim_species:Stim_pupil_movement +
                  (1 | Subject/Trial),  
                  data=prepr.pupil.data, REML=F)
# compare full and reduced model:
library(lmerTest)
as.data.frame(anova(mm1.tobii.red.int, mm1.tobii.full.int, test="F")) #the interaction is not significant, remove it from model
```
```{r}
#fit full model without interaction
mm1.tobii.full<-lmer(Both_Pupil ~ 1 + Stim_pupil_movement + Stim_species + Time + Time_minus_one + I(Time^2)+ I(Time^3) + 
                  Time:Stim_species + I(Time^2):Stim_species + I(Time^3):Stim_species + 
                  Time:Stim_pupil_movement + I(Time^2):Stim_pupil_movement + I(Time^3):Stim_pupil_movement +
                  (1 | Subject/Trial),  
                  data=prepr.pupil.data, REML=F)
                  
#fixed-effect model matrix is rank deficient so dropping 1 column / coefficient
```
```{r}
#full model without int, reml
mm1.tobii.full.reml<-lmer(Both_Pupil ~ 1 + Stim_pupil_movement + Stim_species + Time + Time_minus_one + I(Time^2)+ I(Time^3) + 
                  Time:Stim_species + I(Time^2):Stim_species + I(Time^3):Stim_species + 
                  Time:Stim_pupil_movement + I(Time^2):Stim_pupil_movement + I(Time^3):Stim_pupil_movement +
                  (1 | Subject/Trial),  
                  data=prepr.pupil.data, REML=F)

round(summary(mm1.tobii.full.reml)$coefficients, 3) #stimulus pupil movement not significant

# to get an overall test of the fixed effect of species, compare the full model with a reduced model not comprising
# the effect of stim_species 
# fit the reduced model not comprising the effect of stim_species

library(lme4)
mm1.tobii.red=lmer(Both_Pupil ~ 1 +Stim_pupil_movement + Time + Time_minus_one + I(Time^2)+ I(Time^3) + 
                  Time:Stim_pupil_movement + I(Time^2):Stim_pupil_movement + I(Time^3):Stim_pupil_movement +
                  (1 | Subject/Trial),  
                  data=prepr.pupil.data, REML=F)

# compare full and reduced model:
library(lmerTest)
as.data.frame(anova(mm1.tobii.red, mm1.tobii.full, test="F")) #stimulus species has a significant effect (Chisq. 30.80, df=8, P<.001)
```


```{r}
#Model stability 


```


```{r}
#Stimulus Pupil Movement Plot

prepr.pupil.data.bins<- prepr.pupil.data %>%
  group_by(Time, Stim_pupil_movement) %>%
  summarise(mean.pupil.corrected.binned = mean(pupil.base.corrected, na.rm = TRUE), sd.pupil.corrected.binned= sd(Both_Pupil, na.rm = TRUE), se.pupil.corrected.binned = sd(pupil.base.corrected, na.rm = TRUE) / sqrt(length(pupil.base.corrected)))



pupil.plot <- ggplot(data = prepr.pupil.data.bins, aes(x = Time, y = mean.pupil.corrected.binned)) +
  geom_vline(aes(xintercept=baseline.end), lty=2, alpha=0.3)+
  ylab("Pupil size (a.u.)") +
  xlab("Time (in s)") +
  geom_point(aes(x = Time, y = mean.pupil.corrected.binned, color = Stim_pupil_movement), alpha = 0.3, size = 0.5) +
  geom_ribbon(aes(ymin = mean.pupil.corrected.binned - se.pupil.corrected.binned, ymax = mean.pupil.corrected.binned + se.pupil.corrected.binned, fill = Stim_pupil_movement), alpha = 0.6) +
    xlim(0, 5.8) +
    theme_bw()+
  scale_color_brewer(palette="Dark2")+
  scale_fill_brewer(palette="Dark2")+
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        legend.title = element_text("Stimulus pupil movement"), legend.position = c(0.80, 0.25), legend.text=element_text(size=12),
        axis.text.y=element_text(size=16), axis.text.x=element_text(size=16),
        axis.title=element_text(size=18))+
        labs(color = "Stimulus pupil movement", fill = "Stimulus pupil movement")

pupil.plot
```


```{r}
#Save the Stimulus Pupil Movement plot
ggsave(pupil.plot, filename = "graphs/preprocessed.baseline.corrected.pupil.plot.png", height = 5, width = 8, scale = 0.7, dpi=1200)
```


```{r}
#Stimulus Species Plot

prepr.pupil.data.bins.species<- prepr.pupil.data %>%
  group_by(Time, Stim_species) %>%
  summarise(mean.pupil.corrected.binned = mean(pupil.base.corrected, na.rm = TRUE), sd.pupil.corrected.binned= sd(Both_Pupil, na.rm = TRUE), se.pupil.corrected.binned = sd(pupil.base.corrected, na.rm = TRUE) / sqrt(length(pupil.base.corrected)))



pupil.species.plot <- ggplot(data = prepr.pupil.data.bins.species, aes(x = Time, y = mean.pupil.corrected.binned)) +
  geom_vline(aes(xintercept=baseline.end), lty=2, alpha=0.3)+
  ylab("Pupil size (a.u.)") +
  xlab("Time (in s)") +
  geom_point(aes(x = Time, y = mean.pupil.corrected.binned, color = Stim_species), alpha = 0.3, size = 0.5) +
  geom_ribbon(aes(ymin = mean.pupil.corrected.binned - se.pupil.corrected.binned, ymax = mean.pupil.corrected.binned + se.pupil.corrected.binned, fill = Stim_species), alpha = 0.6) +
    xlim(0, 5.8) +
    ylim(-0.5, 0.4)+
    theme_bw()+
  scale_color_brewer(palette="Dark2")+
  scale_fill_brewer(palette="Dark2")+
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        legend.title = element_text(), legend.position = c(0.80, 0.2), legend.text=element_text(size=12),
        axis.text.y=element_text(size=16), axis.text.x=element_text(size=16),
        axis.title=element_text(size=18))+
        labs(color = "Stimulus species", fill = "Stimulus species")

pupil.species.plot
```


```{r}
#Save the Stimulus Pupil Movement plot
ggsave(pupil.species.plot, filename = "graphs/preprocessed.baseline.corrected.pupil.species.plot.png", height = 5, width = 8, scale = 0.7, dpi=1200)
```
